Postural changes mediate children's visual access to social information

### 2018-01-15 writeup-cogsci-jan14/cogsci2018_faceOnly.Rmd
eval text

author-information: > 
    \author{{\large \bf Alessandro Sanchez} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Bria Long} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
        \And {\large \bf Ally Kraus} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
        \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

### Detector evaluation
In order to evaluate the performance of these detectors, we constructed a "gold set" of frames
Evaluating face detectors (text here about how gold standard was selected)

>>>>

author-information: > 
    \author{{\large \bf Alessandro Sanchez} \\ \texttt{sanchez7@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Bria Long} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
        \And {\large \bf Ally Kraus} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
        \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

### Detector evaluation
In order to evaluate the performance of these detectors, we constructed a "gold set" of frames by hand labeling both a sample of frames with a high density of faces (as reported by the detectors) and a random sample from the remaining frames. This was done so as to not bias our evaluation by the relatively rare appearance of faces in the dataset. A face was present in a frame if at least half of the face was showing. Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of previous measures) were calculated and are reported in Table 2.
Both detectors performed relatively well on the gold set, with MTCNN outperforming OpenPose on the random sample but trailing behind in the high density sample. Due to high performance of these two detectors we have included the results of both in the analyses to follow.

### 2018-01-15 writeup-cogsci-jan14/cogsci2018_faceOnly.tex
eval text

\author{{\large \bf Alessandro Sanchez} \\ \texttt{author1@university.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Bria Long} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Ally Kraus} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

In order to evaluate the performance of these detectors, we constructed
a ``gold set'' of frames Evaluating face detectors (text here about how
gold standard was selected)

>>>>

\author{{\large \bf Alessandro Sanchez} \\ \texttt{sanchez7@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Bria Long} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Ally Kraus} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

In order to evaluate the performance of these detectors, we constructed
a ``gold set'' of frames by hand labeling both a sample of frames with a
high density of faces (as reported by the detectors) and a random sample
from the remaining frames. This was done so as to not bias our
evaluation by the relatively rare appearance of faces in the dataset. A
face was present in a frame if at least half of the face was showing.
Precision (hits / hits + false alarms), recall (hits / hits + misses),
and F-score (harmonic mean of previous measures) were calculated and are
reported in Table 2. Both detectors performed relatively well on the
gold set, with MTCNN outperforming OpenPose on the random sample but
trailing behind in the high density sample. Due to high performance of
these two detectors we have included the results of both in the analyses
to follow.
